---
title: "NEWS"
author: Erik.Leppo@tetratech.com
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

baytrends 1.0.1.9011
===========
* Released - 2018-03-21
* Add detrended.salinity function.
    + Includes revised (smaller) data set (sal) for use with function.
    + Updated data.R for "sal" data.

baytrends 1.0.1.9010
===========
* Released - 2018-03-21
* Add detrended.flow function.
    + Add helper functions as internal functions.
    + Remove detrended flow and salinity data files and vignettes from package.

baytrends 1.0.1.9009
===========
* Released - 2018-03-20
* Update internal functions.
    + mdlKM  -- hide
    + flwAveragePred  -- hide
    + qw.export  -- make visible
    + as.qw-method   -- hide
    + qw-class   -- hide

baytrends 1.0.1.9008
===========
* Released - 2018-03-19
* Update documentation.
    + Vignette
    + data.R
    + baytrends.R
* Code edit in SelectData.R.

baytrends 1.0.1.9007
===========
* Released - 2018-03-16
* Fixes from "check"
    + data.R
    + file size
    + dlimit and censorLevels from smwrQW
    + strip.blanks from smwrGraphs
    
baytrends 1.0.1.9006
===========
* Released - 2018-03-14
* Update qw vignette.

baytrends 1.0.1.9005
===========
* Released - 2018-03-14
* Tweak qw.export and qw.import functions and vignette.

baytrends 1.0.1.9004
===========
* Released - 2018-03-02
* Tweak qw.export Rounding export.
* QW object import internal function, qw.import.
* QW object vignette.

baytrends 1.0.1.9003
===========
* Released - 2018-03-01
* QW object export internal function, qw.export.

baytrends 1.0.1.9002
===========
* Released - 2018-02-28
* More clean up of linked 'see also' references in smwr functions.
* Add help file for package name, baytrends.R.
* Moved detrended salinity and flow vignettes to extdata.
* Rename seasonally detrended data sets (salinity and flow) without special characters.

baytrends 1.0.1.9001
===========
* Released - 2018-02-23
* Clean up after running Check.
    + Move /data-raw to /inst/data-raw
    + Document /data in /R/data.R
    + DESCRIPTION, remove dataRetrieval from Suggests (already under Imports).
    
baytrends 1.0.1
===========
* Released - 2018-02-16
* Clean up and send out to project users.

baytrends 1.0.0.9002
===========
* Released - 2018-02-15
* Add back censoring.R from smwrQW package as it is needed for qw objects.  Was removed in v0.3.3.9016

baytrends 1.0.0.9001
===========
* Released - 2018-02-05
* Improve error trapp for when to allow baytrends to run an intervention model.
    + selectData.R
    + gamTest.R

baytrends 1.0.0
===========
* Released - 2018-02-01
* Set as release on GitHub.

baytrends 0.3.3.9019
===========
* Released - 2018-02-01
* Update vignettes.  Remove setwd().

baytrends 0.3.3.9018
===========
* Released - 2018-02-01
* Updated Vignettes to run with data in vignettes folder.
* Added function fillMissing from smwrBase for detrended flow vignette.

baytrends 0.3.3.9017
===========
* Released - 2018-01-31
* Fix errors in Namespace noted in Check.

baytrends 0.3.3.9016
===========
* Released - 2018-01-31
* Remove unneeded functions from smwrQW package.

baytrends 0.3.3.9015
===========
* Released - 2018-01-31
* Created vignettes:
    + QW object conversion
    + Detrended flow data
    + Detrended salinity data
* Add and remove funtions from index with keyword internal.

baytrends 0.3.3.9014
===========
* Released - 2018-01-12
* Add more functions, as.x, to keywords internal to remove from help file list.
* Add Erik W Leppo as author in DESCRIPTION.

baytrends 0.3.3.9013
===========
* Released - 2018-01-11
* Modified dataCensored to include timezone.  Should fluctuate between EST and EDT.
    + Exported original data file with TZ included with smwrQW present.  Then rebuilt dataCensored with smwrQW removed.

baytrends 0.3.3.9012
===========
* Released - 2018-01-05
* Fix files names.  OneDrive on development computer introduced duplicate files.  Some of older versions.
* Hid all smwr*.R files from help file index with keywords internal.

baytrends 0.3.3.9011
===========
* Released - 2017-12-20
* dataCensored
    + Clean up "data-raw" folder and GenerateData script.
    + Overwrite smwrQW dependant dataCensored.rda file with baytrends version.
    + Remove dataCensored CSV files from \inst\extdata.
* Move 
* Rename temporary R scripts from "x_*" to "smwrQW_x_*".
    + Known files that are needed already have smwrQW prefix.  Keep new ones different.


baytrends 0.3.3.9010
===========
* Released - 2017-12-19
* Rebuild with minor edits for smwrQW references in files (Find in Files).
* Added smwrQW_is.na.R.
* Edits to _GenerateData_dataCensored.R.
    + qw object creates but still fails when adding to data.frame.
* Copy in all smwrQW function not already added.  Test if builds.

baytrends 0.3.3.9009
===========
* Released - 2017-12-06
* Added function as.qw from smwrQW.
    + Modified include from qw-class.R to a1_smwrQW_qw-class.R.
    + Did not add as.lcens or as.mcens as they require other functions in smwrBase and smwrQW.
* Added "data-raw" folder.
* Created all parts of dataCensored object and saved to "data-raw".
* Added script to build dataCensored.
* Renamed back to baytrends on GitHub and in development code.
* a1_smwrQW_qw-class.R
    + Comment out "name" 
* as.qw.R
    + Comment out "See Also" (refers to function not ported from smwrQW).

baytrends 0.3.3.9008
===========
* Released - 2017-12-05
* Resave dataCensored.rda.  Installed smwrQW so could open and resets "qw" class to first reference in namespace (baytrends).  Then saved and removed smwr packages.
* Add lscens class as well; a2_smwrQW_lcens-class.R.
* Rename mscens from a2 to a3 to preserve collate order of smwrQW.

baytrends 0.3.3.9007
===========
* Released - 2017-12-05
* Rename new class objects to appear in R folder first.  And will load first.
    + 'smwrQW_qw-class.R' (prefix "a1_").
    + 'smwrQW_mcens-class.R' (prefix "a2_").
* Need to fix functions and examples that are looking for smwrQW.
    + analysisOrganizeData
    + selectData
    + gamDiff
    + gamTest

baytrends 0.3.3.9006
===========
* Released - 2017-12-05
* Removed swmr packages from R install.
* Rebuild baytrends with smwrBase functions included.
    + baseDay
    + baseDay2decimal
* Removed import from smwrQW from gamTest. Had import for smwrQW.
* Added class objects qw and mcens from smwrQW.
* Renamed all added R files with smwrBase_ or smwrQW_.

baytrends 0.3.3.9005
===========
* Released - 2017-12-05
* Remove all smwrX packages (Base, Graphs, QW, and Stats).  Not just the oprhaned QW and Stats.  Base and Graphs DEPEND on QW as well.

baytrends 0.3.3.9004
===========
* Released - 2017-12-04
* Modified NEWS to NEWS.rmd.

baytrends 0.3.3.9003
===========
* Released - 2017-12-04
* Remove "smwrQW" from Depends in DESCRIPTION.
* Remove "smwrStats" from Suggests in DESCRIPTION.

baytrends 0.3.3.9002
===========
* Released - 2017-12-04
* Add Notebooks for Library Creation and Testing to \inst\extdata.

baytrends 0.3.3.9001
===========
* Released - 2017-12-04
* Renamed to baytrends033
* Test version to GitHub

baytrends 0.3.3
===========
* Released - 11/24/2017
* Updated gamDiff: flow/salinity model to calculate baseline/current mean differences based on average conditions
* Updated gamPlotDisp: corrected full model display option

baytrends 0.3.2
===========
* Released - 8/09/2017
* Updated seasonal model to include averaging over season and flow[salinity]

baytrends 0.3.1
===========
* Released - 8/6/2017
* Added function loadExcel to facilitate reading user Excel files. Similar functionality to the existing function loadData.
* Changed nomenclature from tidalStations to stationMasterList
* Enhanced knot specification to allow 2 levels of knots (gamK1 and gamK2). Previously only could specify gamK_CritSel. Specification of gamK1 and gamK2 now included as part of specifying gamModels
* Enhanced to allow for including flow or salinity as an independent variable in gam models, including adding gam4 to default list of gam models evaluated. (**Does** not include updated for computing seasonally averaged/flow[salinity] averaged model in this version.)

baytrends 0.2.7
===========
* Released - 7/20/2017
* Enhanced baytrends to output p-values and estimates of change related to laboratory method changes (“interventions”) in a style that compares method “A” to “B”, “B” to “C”, “C” to “D”, etc. rather than “A” to “B”, “A” to “C”, “A” to “D”, etc.

baytrends 0.2.6
===========
* Released - 4/25/2017
* corrected usage of user specified station file

baytrends 0.2.5
===========
* Released - 3/15/2017
* updated loadData to allow for specifying strings indicating null values, see naChar
* updated multiple functions to address 'no visible binding for global variable' notes
* added @importFrom statements for graphics and stat functions

baytrends 0.2.4
===========
* Released - 2/9/2017
* updated seasonal average model algorithm to be independent of mn.doy
* added algorithm to compute number of knots in s(cyear) term based on record length
* added user ability to set 'select' term in mgcv::gam function to TRUE, FALSE, or algorithm selected
* added user ability to set expectation maximization convergence threshold
* added F-stat evaluation and ANOVA table modification


baytrends 0.2.3
===========
* Released - 11/09/2016
* Documentation updated
* Added default settings to for gam formula for intervention testing
* Added functionality to trim early data where the level of censoring exceeds desired levels
* Added functionality to thin prediction data set to improve speed and reduce the size of the returned results
* loadData: added functionality to convert date-like fields to POSIXct format (see argument convDates)
* Add error trap for when all data associated with dependent variable are NA

baytrends 0.2.2
===========
* Released - 10/17/2016
* Updated graphics for censored data

baytrends 0.2.1
===========
* Original release - 10/13/2016
