---
title: "NEWS"
author: Erik.Leppo@tetratech.com
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

v0.3.3.9008
===========
* 2017-12-05
* Resave dataCensored.rda.  Installed smwrQW so could open and resets "qw" class to first reference in namespace (baytrends).  Then saved and removed smwr packages.
* Add lscens class as well; a2_smwrQW_lcens-class.R.
* Rename mscens from a2 to a3 to preserve collate order of smwrQW.

v0.3.3.9007
===========
* 2017-12-05
* Rename new class objects to appear in R folder first.  And will load first.
    + 'smwrQW_qw-class.R' (prefix "a1_").
    + 'smwrQW_mcens-class.R' (prefix "a2_").
* Need to fix functions and examples that are looking for smwrQW.
    + analysisOrganizeData
    + selectData
    + gamDiff
    + gamTest

v0.3.3.9006
===========
* 2017-12-05
* Removed swmr packages from R install.
* Rebuild baytrends with smwrBase functions included.
    + baseDay
    + baseDay2decimal
* Removed import from smwrQW from gamTest. Had import for smwrQW.
* Added class objects qw and mcens from smwrQW.
* Renamed all added R files with smwrBase_ or smwrQW_.

v0.3.3.9005
===========
* 2017-12-05
* Remove all smwrX packages (Base, Graphs, QW, and Stats).  Not just the oprhaned QW and Stats.  Base and Graphs DEPEND on QW as well.

v0.3.3.9004
===========
* 2017-12-04
* Modified NEWS to NEWS.rmd.

v0.3.3.9003
===========
* 2017-12-04
* Remove "smwrQW" from Depends in DESCRIPTION.
* Remove "smwrStats" from Suggests in DESCRIPTION.

v0.3.3.9002
===========
* 2017-12-04
* Add Notebooks for Library Creation and Testing to \inst\extdata.

v0.3.3.9001
===========
* 2017-12-04
* Renamed to baytrends033
* Test version to GitHub

baytrends 0.3.3
===========
* Released - 11/24/2017
* Updated gamDiff: flow/salinity model to calculate baseline/current mean differences based on average conditions
* Updated gamPlotDisp: corrected full model display option

baytrends 0.3.2
===========
* Released - 8/09/2017
* Updated seasonal model to include averaging over season and flow[salinity]

baytrends 0.3.1
===========
* Released - 8/6/2017
* Added function loadExcel to facilitate reading user Excel files. Similar functionality to the existing function loadData.
* Changed nomenclature from tidalStations to stationMasterList
* Enhanced knot specification to allow 2 levels of knots (gamK1 and gamK2). Previously only could specify gamK_CritSel. Specification of gamK1 and gamK2 now included as part of specifying gamModels
* Enhanced to allow for including flow or salinity as an independent variable in gam models, including adding gam4 to default list of gam models evaluated. (**Does** not include updated for computing seasonally averaged/flow[salinity] averaged model in this version.)

baytrends 0.2.7
===========
* Released - 7/20/2017
* Enhanced baytrends to output p-values and estimates of change related to laboratory method changes (“interventions”) in a style that compares method “A” to “B”, “B” to “C”, “C” to “D”, etc. rather than “A” to “B”, “A” to “C”, “A” to “D”, etc.

baytrends 0.2.6
===========
* Released - 4/25/2017
* corrected usage of user specified station file

baytrends 0.2.5
===========
* Released - 3/15/2017
* updated loadData to allow for specifying strings indicating null values, see naChar
* updated multiple functions to address 'no visible binding for global variable' notes
* added @importFrom statements for graphics and stat functions

baytrends 0.2.4
===========
* Released - 2/9/2017
* updated seasonal average model algorithm to be independent of mn.doy
* added algorithm to compute number of knots in s(cyear) term based on record length
* added user ability to set 'select' term in mgcv::gam function to TRUE, FALSE, or algorithm selected
* added user ability to set expectation maximization convergence threshold
* added F-stat evaluation and ANOVA table modification


baytrends 0.2.3
===========
* Released - 11/09/2016
* Documentation updated
* Added default settings to for gam formula for intervention testing
* Added functionality to trim early data where the level of censoring exceeds desired levels
* Added functionality to thin prediction data set to improve speed and reduce the size of the returned results
* loadData: added functionality to convert date-like fields to POSIXct format (see argument convDates)
* Add error trap for when all data associated with dependent variable are NA

baytrends 0.2.2
===========
* Released - 10/17/2016
* Updated graphics for censored data

baytrends 0.2.1
===========
* Original release - 10/13/2016
