---
title: "NEWS"
author: Erik.Leppo@tetratech.com and jon.harcum@tetratech.com
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r Options, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r LastUpdate, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```
baytrends 1.1.0.9004
===========
* Release 2019-06-25
* Minor punch list issues from v*.9003 and .9002. Add option analySpec$showGamNumOnPlot to add gam # onto plot

baytrends 1.1.0.9003
===========
* Release 2019-06-06
* Improved error trapping related to required station and parameter list fields. Added detrended salinity, detrended flow and method list warnings.

baytrends 1.1.0.9002
===========
* Release 2019-05-31
* Added functions gamTestSeasonal and gamPlotDispSeasonal to compute and only display a seasonal mean for a single date or for a date range.

baytrends 1.1.0
===========
* Release 2019-03-14
* Release update for CRAN
    + As minor upgrade.

baytrends 1.0.8
===========
* Release 2019-03-14
* Release update for CRAN
    + As bug fix.

baytrends 1.0.7.9011
===========
* Release 2019-03-14
* Fix date in DESCRIPTION.
* Add library creation notebook to .Rbuildignore

baytrends 1.0.7.9010
===========
* Release 2019-03-13
* Updates based on "check" to prepare for submittal to CRAN.
    + Added some oxygen tags
    + Added .install_extras to vignettes folder for additional PDF docs
    + "dot" prefix functions with keyword internal
    + Removed example for hidden function .createResiduals
    + .findFile examples marked as do not run.

baytrends 1.0.7.9009
===========
* Release 2019-03-11
* Update from devtools::session_info to sessioninfo::session_info.  Issue #31.
    + closeOut function.
* Rebuild vignettes.
    + Names not showing in help file.

baytrends 1.0.7.9008
===========
* Release 2019-03-05 
* seasMeandoy.xyz removed from prediction data set

baytrends 1.0.7.9007
===========
* Release 2018-12-28 
* Based on date range entered into analySpec_gamLegend_legend for analySpec_gamLegend_descrip equal to 'seasMean', compute predicted values based on doy's spread across above date range. seasMeandoy.xyz maintained in prediction data set along with seasMeanMin, seasMeanMean, and seasMeanMax.

baytrends 1.0.7.9006
===========
* Release 2018-08-08 
* created loadModelsResid function to include models for calculating residuals (i.e., primarily gam4 and gam5 without cyear)
* updated createResidual to save plots to file

baytrends 1.0.7.9005
===========
* Release 2018-08-03 
* updated createResidual to skip over cases (i.e., specific stations) where there were insufficient data to run specified gam formula

baytrends 1.0.7.9004 
===========
* Release 2018-08-01 
* added loadModels function to facilitate gam formula specification; updated createResidual to include a "fall back" option to use gam2 or gam4 if user had selected gam3 or gam5 and the model did not run (expected due to intervention)

baytrends 1.0.7.9003
===========
* Release 2018-07-30
* function deSeasonalize renamed to createResiduals; extended to allow for any gam0-gam5 model

baytrends 1.0.7.9002
===========
* Release 2018-07-18
* update function deSeasonalize to allow for s(doy) and perform basic testing

baytrends 1.0.7.9001
===========
* Release 2018-07-13
* added function deSeasonalize

baytrends 1.0.7
===========
* Release 2018-07-12
* Resubmit to CRAN

baytrends 1.0.6.9001
===========
* Release 2018-07-12
* DESCRIPTION
    + Additional_repositories to URL
    + Update and lengthen Description.

baytrends 1.0.6
===========
* Release 2018-07-09
* Resubmit to CRAN
=======
baytrends 1.0.5.9002
===========
* Release 2018-07-11
* Update ANOVA table to allow for no parametric terms in gam formula

baytrends 1.0.5.9001
===========
* Release 2018-07-09
* Fix CRAN submission NOTES
    + Restructure my names with middle initial as maintainer.
    + donotrun on examples for detrended.flow and detrended.salinity

baytrends 1.0.5
===========
* Released 2018-07-06
* Create "release" on GitHub.
* Submit to CRAN

baytrends 1.0.4.9012
===========
* Released 2018-07-06
* selectData
    + Remove example.
* CHECK
    + 0 errors | 0 warnings | 0 notes

baytrends 1.0.4.9011
===========
* Released 2018-07-06
* DESCRIPTION
    + Change "maintainer" from Jon Harcum to Erik Leppo so Erik can submit to CRAN.
    + Change "additional repositories" to GitHub.  Was http://owi.usgs.gov/R.
* .Rbuildignore
    + Add cran-comments.md
* qw.import; example qw.names
    + Rename variables without "f"; po4, no23, and nh4
    + Remove variables pp and pn.
* detrended.flow
    + Fix CHECK NOTE for figNum.
    + Added "figNum" to globalVariables in zzz.R
    + Assigned figNum as NULL before assign as zero.
* dataCensored
    + Fix CHECK WARNING
* selectData
    + Example not working.  Mark as "donotrun" while troubleshoot.

baytrends 1.0.4.9010
===========
* Released 2018-07-05
* Add .github to .Rbuildignore to avoid CHECK note.
* Added dates to NEWS releases.
* Update data.R for dataCensored.

baytrends 1.0.4.9009
===========
* Released 2018-07-03
* dataCensored: aligned data set with companion journal article

baytrends 1.0.4.9008
===========
* Released 2018-07-03
* dataCensored: aligned data set with companion journal article

baytrends 1.0.4.9007
===========
* Released 2018-07-02
* selectData: improved error trap for lack of data

baytrends 1.0.4.9006
===========
* Released 2018-6-12
* updated documentation 

baytrends 1.0.4.9005
===========
* Released 2018-6-12
* Added baytrends version to to iSpec and improved readme file

baytrends 1.0.4.9004
===========
* Released 2018-6-12
* Added list of seasonal models to iSpec  

baytrends 1.0.4.9003
===========
* Released 2018-6-12
* Updated impute function to include maximum likelihood estimation assuming normal and lognormal distribution

baytrends 1.0.4.9002
===========
* Released 2018-6-12
* Updated NEWS and DESCRIPTION.
* Updated online documentation for analysisOrganizeData function
* pass parameterList from gamTest to .chkParameter

baytrends 1.0.4.9001
===========
* Released 2018-6-12
* Updated NEWS and DESCRIPTION.
* Updated online documentation for analysisOrganizeData function
* pass parameterList from gamTest to .chkParameter

baytrends 1.0.4
===========
* Released 2018-05-14
* Created release 1.0.4 on GitHub

baytrends 1.0.3.9021
===========
* Released 2018-05-14
* Updated NEWS and DESCRIPTION.
* Check results: no errors, warnings, or notes.

baytrends 1.0.3.9020
===========
* Released 2018-05-13
* GitHub commit; Merge pull request #16 from tetratech/12Mar2018

baytrends 1.0.3.9019
===========
* Released 2018-05-13
* GitHub commit; v1.0.3.9011
* missed layerLukup -> layerList naming convention

baytrends 1.0.3.9019
===========
* Released 2018-05-12
* GitHub commit; Merge pull request #15 from tetratech/12Mar2018 

baytrends 1.0.3.9018
===========
* Released 2018-05-12
* GitHub commit; v1.0.4
    
baytrends 1.0.3.9017
===========
* Released 2018-05-12
* GitHub commit; v1.0.4

baytrends 1.0.3.9016
===========
* Released 2018-05-12
* GitHub commit; v1.0.4
* Added passing of salinity.detrended and flow.detrended to gamTest
* Added passing stationMasterList, parameterList, and layerLukup to analyzeOrganizeData
* Corrected getUSGSflow function to accomodate missing values at beginning/ending of record
* Moved package `plyr` from Suggests to Imports in DESCRIPTION
* Remaining Check issue with no visible binding for global variable; salinity.detrended
    + .gamPlotCalc
    + .mergeSalinity
    + gamDiff

baytrends 1.0.3.9015
===========
* Released 2018-05-12
* GitHub commit; Merge pull request #14 from tetratech/detrended_files 
* Detrended files
    
baytrends 1.0.3.9014
===========
* Released 2018-05-12
* GitHub commit; v1.0.3.9009
* Set data frames for station and layer list to not use factors
    
baytrends 1.0.3.9013
===========
* Released 2018-05-12
* GitHub commit; v1.0.3.9009
* Further clean up for handling detrended files.
    
baytrends 1.0.3.9012
===========
* Released 2018-05-12
* GitHub commit; v1.0.3.9009
* Migrate gamDiff for detrended flow and salinity.
    
baytrends 1.0.3.9011
===========
* Released 2018-05-12
* GitHub commit; v1.0.3.9008
* analysisOrganizeData: add parameterList, stationMasterList, and layerLukup to argument list. If not passed then default baytrend data frames are used.  added parmRecensor to depVarList, added usgsGageName to stationList
* selectData:  migrated from using stationMasterList, parameterList to stationList and depVarList.
* gamTest: added salinity.detrended to argument list, updated conditionals used to skip flw_sal models, embedded explicit passing of flow.detrended and salinity.detrended to mergeFlow and mergeSalinity.

baytrends 1.0.3.9010
===========
* Released 2018-05-12
* GitHub commit; documentation typographical error correction
    
baytrends 1.0.3.9009
===========
* Released 2018-05-11
* GitHub commit; Merge pull request #11 from tetratech/fix_flow_retrieval
    
baytrends 1.0.3.9008
===========
* Released 2018-05-11
* GitHub commit; v1.0.3.9005
* updated getUSGSflow function to fill in missing flow values at the beginning and ending of time series.
    
baytrends 1.0.3.9007
===========
* Released 2018-05-11
* GitHub commit; Merge pull request #10 from tetratech/fix_flow_retrieval

baytrends 1.0.3.9006
===========
* Released 2018-05-011
* GitHub commit; v1.0.3.9005
* updated getUSGSflow function to fill in missing flow values at the beginning and ending of time series.
    
baytrends 1.0.3.9005
===========
* Released 2018-05-09
* GitHub commit; Merge pull request #8 from tetratech/harcum_development
    
baytrends 1.0.3.9004
=========== 
* Released 2018-05-09
* GitHub commit; v1.0.3.9004
    
baytrends 1.0.3.9003
===========    
* Released 2018-05-07
* GitHub commit; v1.0.3.9003
* Last fix for Check.  Ready for sumittal to CRAN.  Issue #1

baytrends 1.0.3.9002
===========   
* Released 2018-05-07
* GitHub commit; v1.0.3.9002
* Verified merge of DEV branch into Master.  
* Fixed an issue with plyr and 
* Re-ran Check to get ready for CRAN submittal (Issue #1 ).

baytrends 1.0.3.9001
===========
* Released 2018-05-07
* Merge Development Branch (v.0.2.9012 DEV) with master branch.
* Resolve conflicts:
    + DESCRIPTION
    + NAMESPACE
    + NEWS (left alone as will rebuild)
    + NEWS.rmd
    + mergeFlow.R
    + baytrends_LibraryCration.nb.html (left alone as will rebuild)

baytrends 1.0.2.9012, development branch
===========
* Released - 2018-05-03
* branch of master based on v1.0.2 (release)
* Clean up from check for CRAN
* Note; NEWS.rmd.  Add to git.ignore and .Rbuildignore
* Error; sensAdjflow2.R "figNum".  Add QC check to ensure is defined.
* Warning; undocumented dataset; added param and default to mergeFlow, gamTest, gamPlotCalc, and gamDiff.  Also added to data.R (was missing).
* Note; Namespace, importFrom.
    + importFrom("stats", "BIC", "StructTS", "aggregate", "approx",
             "cov2cor", "dnorm", "filter", "fitted", "hat", "integrate",
             "logLik", "lowess", "lsfit", "na.omit", "na.pass",
             "naresid", "pchisq", "ppoints", "qf", "residuals", "sd",
             "tsSmooth", "update", "var")
   + importFrom("utils", "flush.console", "getS3method", "modifyList",
             "read.table", "strOptions", "write.table")
* Added QC to define figNum.  
    + Copied from seasAdjflow2.R to detrended.flow.R and detrended.salinity.R
* Add functions from swmwr packages:
    + smwrBase; %cn%, group2row, isDateLike
    + smwrQW; mcenKM, mcenMLE, mcenROS, mdlMLE, mdlROS, pcodeNWISqw
    + smwrStats; rmse, vif
* Adding the above led to others that needed to be added:
    + smwrGraphs; refLine, xyPlot
    + smwrBase; importRDB
* Addition of xyPlot required more functions:
    + smwrGraphs; setPlot, linearPretty, setPage, timePlot, colorPlot
* Remove cross references in "seealso" for some of the imported smwr functions.
    + importRDB, isLike, linearPretty, refLinem, setPage, setplot, timePlot, cn
* importFrom needed for 3 more packages in the newest smwr functions that were added.
    + importFrom("grDevices", "Type1Font", "dev.cur", "extendrange", "gray",
             "pdfFonts", "rainbow")
    + importFrom("graphics", "box", "segments", "strwidth")
    + importFrom("stats", "cov.wt", "dist", "model.matrix")
* Add more smwr package functions:
    + Base; dectime, dectime2Date 
    + Graphs; datePretty, namePretty, numericData, setColor, setGD, setMargin
    , setMultiPlot, timePretty
* Fix links in most recently added functions; comment out seealso.
    + datePretty, dectime, namePretty, setColor, setMargin, setMultiPlot 
* Add importFrom; grDevices colors
* Add function from smwr packages;
    + smwrGraphs; month.USGS, renderPretty, setExplan, transData, linewt (framewt)
* Add importFrom for the newly added functions.
    + importFrom("grDevices", "col2rgb", "rgb")
    + importFrom("graphics", "axis")
* Add function from smwr packages;
    + smwrGraphs; addCaption
* Fix "assign" to global environment in smwrGraphs_setPage.R
    + Line 180, comment out.  Is setting to NULL as a precaution but function isn't used by baytrends.
* Data with "no visible bindig for global variable" error.
    + Add a line at the beginning of each affected function to reference the data; baytrends::xyz.
    + Peter Dalgaard's proposed solution, 2014-Aug
    + http://r.789695.n4.nabble.com/no-visible-binding-for-global-variable-for-data-sets-in-a-package-td4696053.html
    + .chkParameter; parameterList
    + analysisOrganizeData; parameterList, stationMasterList, layerLukup
    + selectData; stationMasterList, parameterList, layerLukup
* gamDiff, bad usage of stat.  Undefined.  Line 193.
    + Change to iSpec$stat
* Remaining issues:
    + .gamPlotCalc; salinity.detrended
    + .mergeSalinity; salinity.detrended
    + gamDiff; salinity.detrended
    
baytrends 1.0.2.9011
===========
* Released - 2018-05-02
* v1.0.2.9002
* add standard error to stat.gam.result and chng.gam.result output
* add USGS gage ID and name to stat.gam.result and chng.gam.result output
* add mgcvOK to stat.gam.result and chng.gam.result output to indicate if mgcv::gam ran ok
* removed median as option for summarizing data across layers
* expose impute function for simple substitution (0, 1/2dl, dl) conversion of qw data to vector
* added error handling to trap mgcv::gam non-convergence errors
    
=======
baytrends 1.0.3
===========
* Released - 2018-05-03
* Release version

baytrends 1.0.2.9013
===========
* Released - 2018-05-03
* Fix lubridate and plyr conflict.  Issue #6.
    + gamTest change import lubridate mgcv plyr to 
    importFrom for lubridate mdy and plyr  rbind.fill.

baytrends 1.0.2.9012
===========
* Released - 2018-05-03
* Update versioning in NEWS and DESCRIPTION

baytrends 1.0.2.9011
===========
* Released - 2018-05-02
* v1.0.2.9002 in DESCRIPTION
* v1.0.3.0000 in NEWS
* Updates: 
    + add standard error to stat.gam.result and chng.gam.result output
    + add USGS gage ID and name to stat.gam.result and chng.gam.result output
    + add mgcvOK to stat.gam.result and chng.gam.result output to indicate if mgcv::gam ran ok
    + removed median as option for summarizing data across layers
    + expose impute function for simple substitution (0, 1/2dl, dl) conversion of qw data to vector
    + added error handling to trap mgcv::gam non-convergence errors

baytrends 1.0.2.9010
===========
* Released - 2018-05-02
* v1.0.2.9002
* add intervention label to GAM Parameter Coefficient table.

baytrends 1.0.2.9009
===========
* Released - 2018-05-02
* v1.0.2.9002
* Added error trapping to address non-convergence of mgcv::gam

baytrends 1.0.2.9007
===========
* Released - 2018-05-01
* Merge branch 'master' of https://github.com/tetratech/baytrends 

baytrends 1.0.2.9006
===========
* Released - 2018-05-01
* corrected storage of usgs codes

baytrends 1.0.2.9005
===========
* Released - 2018-05-01
* documentation updates
    
baytrends 1.0.2.9004
===========
* Released - 2018-05-01
* documentation updates

baytrends 1.0.2.9004
===========
* Released - 2018-05-01
* documentation updates

baytrends 1.0.2.9003
===========
* Released - 2018-05-01
* only allow 'mean' for computing layer aggregation.

baytrends 1.0.2.9002
===========
* Released - 2018-05-01
*  added usgs gage id, usgs gage name, and gam diff standard error to to stat.gam.result and chng.gam.result output data sets

baytrends 1.0.2.9001
===========
* Released - 2018-05-01
* exposed impute function; updated impute function to focus on simple substitution

baytrends 1.0.2.0000
===========
* Released - 2018-03-26
* Release version

baytrends 1.0.1.9015
===========
* Released - 2018-03-26
* Function Updates
    + detrended.flow
    + detrended.salinity
* Update detrended vignette for changes in functions.
* Updates from "check".

baytrends 1.0.1.9014
===========
* Released - 2018-03-26
* Update vignettes
    + /docs/baytrends_overview.pdf
    + /vignettes/vignette_qw.Rmd
* New vignette
    + /vignettes/create_Seasonally_Detrended_Flow_and_Salinity_Data_Sets.Rmd
* Update detrended.salinity.R for changes in names in "sal" data.

baytrends 1.0.1.9013
===========
* Released - 2018-03-26
* salinity data.
    + _GenerateData_sal.R
    + sal.rda
    + data.R

baytrends 1.0.1.9012
===========
* Released - 2018-03-21
* Add baytrends_overview.pdf to "doc" as vignette.
    
baytrends 1.0.1.9011
===========
* Released - 2018-03-21
* Add detrended.salinity function.
    + Includes revised (smaller) data set (sal) for use with function.
    + Updated data.R for "sal" data.

baytrends 1.0.1.9010
===========
* Released - 2018-03-21
* Add detrended.flow function.
    + Add helper functions as internal functions.
    + Remove detrended flow and salinity data files and vignettes from package.

baytrends 1.0.1.9009
===========
* Released - 2018-03-20
* Update internal functions.
    + mdlKM  -- hide
    + flwAveragePred  -- hide
    + qw.export  -- make visible
    + as.qw-method   -- hide
    + qw-class   -- hide

baytrends 1.0.1.9008
===========
* Released - 2018-03-19
* Update documentation.
    + Vignette
    + data.R
    + baytrends.R
* Code edit in SelectData.R.

baytrends 1.0.1.9007
===========
* Released - 2018-03-16
* Fixes from "check"
    + data.R
    + file size
    + dlimit and censorLevels from smwrQW
    + strip.blanks from smwrGraphs
    
baytrends 1.0.1.9006
===========
* Released - 2018-03-14
* Update qw vignette.

baytrends 1.0.1.9005
===========
* Released - 2018-03-14
* Tweak qw.export and qw.import functions and vignette.

baytrends 1.0.1.9004
===========
* Released - 2018-03-02
* Tweak qw.export Rounding export.
* QW object import internal function, qw.import.
* QW object vignette.

baytrends 1.0.1.9003
===========
* Released - 2018-03-01
* QW object export internal function, qw.export.

baytrends 1.0.1.9002
===========
* Released - 2018-02-28
* More clean up of linked 'see also' references in smwr functions.
* Add help file for package name, baytrends.R.
* Moved detrended salinity and flow vignettes to extdata.
* Rename seasonally detrended data sets (salinity and flow) without special characters.

baytrends 1.0.1.9001
===========
* Released - 2018-02-23
* Clean up after running Check.
    + Move /data-raw to /inst/data-raw
    + Document /data in /R/data.R
    + DESCRIPTION, remove dataRetrieval from Suggests (already under Imports).
    
baytrends 1.0.1
===========
* Released - 2018-02-16
* Clean up and send out to project users.

baytrends 1.0.0.9002
===========
* Released - 2018-02-15
* Add back censoring.R from smwrQW package as it is needed for qw objects.  Was removed in v0.3.3.9016

baytrends 1.0.0.9001
===========
* Released - 2018-02-05
* Improve error trapp for when to allow baytrends to run an intervention model.
    + selectData.R
    + gamTest.R

baytrends 1.0.0
===========
* Released - 2018-02-01
* Set as release on GitHub.

baytrends 0.3.3.9019
===========
* Released - 2018-02-01
* Update vignettes.  Remove setwd().

baytrends 0.3.3.9018
===========
* Released - 2018-02-01
* Updated Vignettes to run with data in vignettes folder.
* Added function fillMissing from smwrBase for detrended flow vignette.

baytrends 0.3.3.9017
===========
* Released - 2018-01-31
* Fix errors in Namespace noted in Check.

baytrends 0.3.3.9016
===========
* Released - 2018-01-31
* Remove unneeded functions from smwrQW package.

baytrends 0.3.3.9015
===========
* Released - 2018-01-31
* Created vignettes:
    + QW object conversion
    + Detrended flow data
    + Detrended salinity data
* Add and remove funtions from index with keyword internal.

baytrends 0.3.3.9014
===========
* Released - 2018-01-12
* Add more functions, as.x, to keywords internal to remove from help file list.
* Add Erik W Leppo as author in DESCRIPTION.

baytrends 0.3.3.9013
===========
* Released - 2018-01-11
* Modified dataCensored to include timezone.  Should fluctuate between EST and EDT.
    + Exported original data file with TZ included with smwrQW present.  Then rebuilt dataCensored with smwrQW removed.

baytrends 0.3.3.9012
===========
* Released - 2018-01-05
* Fix files names.  OneDrive on development computer introduced duplicate files.  Some of older versions.
* Hid all smwr*.R files from help file index with keywords internal.

baytrends 0.3.3.9011
===========
* Released - 2017-12-20
* dataCensored
    + Clean up "data-raw" folder and GenerateData script.
    + Overwrite smwrQW dependant dataCensored.rda file with baytrends version.
    + Remove dataCensored CSV files from \inst\extdata.
* Move 
* Rename temporary R scripts from "x_*" to "smwrQW_x_*".
    + Known files that are needed already have smwrQW prefix.  Keep new ones different.


baytrends 0.3.3.9010
===========
* Released - 2017-12-19
* Rebuild with minor edits for smwrQW references in files (Find in Files).
* Added smwrQW_is.na.R.
* Edits to _GenerateData_dataCensored.R.
    + qw object creates but still fails when adding to data.frame.
* Copy in all smwrQW function not already added.  Test if builds.

baytrends 0.3.3.9009
===========
* Released - 2017-12-06
* Added function as.qw from smwrQW.
    + Modified include from qw-class.R to a1_smwrQW_qw-class.R.
    + Did not add as.lcens or as.mcens as they require other functions in smwrBase and smwrQW.
* Added "data-raw" folder.
* Created all parts of dataCensored object and saved to "data-raw".
* Added script to build dataCensored.
* Renamed back to baytrends on GitHub and in development code.
* a1_smwrQW_qw-class.R
    + Comment out "name" 
* as.qw.R
    + Comment out "See Also" (refers to function not ported from smwrQW).

baytrends 0.3.3.9008
===========
* Released - 2017-12-05
* Resave dataCensored.rda.  Installed smwrQW so could open and resets "qw" class to first reference in namespace (baytrends).  Then saved and removed smwr packages.
* Add lscens class as well; a2_smwrQW_lcens-class.R.
* Rename mscens from a2 to a3 to preserve collate order of smwrQW.

baytrends 0.3.3.9007
===========
* Released - 2017-12-05
* Rename new class objects to appear in R folder first.  And will load first.
    + 'smwrQW_qw-class.R' (prefix "a1_").
    + 'smwrQW_mcens-class.R' (prefix "a2_").
* Need to fix functions and examples that are looking for smwrQW.
    + analysisOrganizeData
    + selectData
    + gamDiff
    + gamTest

baytrends 0.3.3.9006
===========
* Released - 2017-12-05
* Removed swmr packages from R install.
* Rebuild baytrends with smwrBase functions included.
    + baseDay
    + baseDay2decimal
* Removed import from smwrQW from gamTest. Had import for smwrQW.
* Added class objects qw and mcens from smwrQW.
* Renamed all added R files with smwrBase_ or smwrQW_.

baytrends 0.3.3.9005
===========
* Released - 2017-12-05
* Remove all smwrX packages (Base, Graphs, QW, and Stats).  Not just the oprhaned QW and Stats.  Base and Graphs DEPEND on QW as well.

baytrends 0.3.3.9004
===========
* Released - 2017-12-04
* Modified NEWS to NEWS.rmd.

baytrends 0.3.3.9003
===========
* Released - 2017-12-04
* Remove "smwrQW" from Depends in DESCRIPTION.
* Remove "smwrStats" from Suggests in DESCRIPTION.

baytrends 0.3.3.9002
===========
* Released - 2017-12-04
* Add Notebooks for Library Creation and Testing to \inst\extdata.

baytrends 0.3.3.9001
===========
* Released - 2017-12-04
* Renamed to baytrends033
* Test version to GitHub

baytrends 0.3.3
===========
* Released - 11/24/2017
* Updated gamDiff: flow/salinity model to calculate baseline/current mean differences based on average conditions
* Updated gamPlotDisp: corrected full model display option

baytrends 0.3.2
===========
* Released - 8/09/2017
* Updated seasonal model to include averaging over season and flow[salinity]

baytrends 0.3.1
===========
* Released - 8/6/2017
* Added function loadExcel to facilitate reading user Excel files. Similar functionality to the existing function loadData.
* Changed nomenclature from tidalStations to stationMasterList
* Enhanced knot specification to allow 2 levels of knots (gamK1 and gamK2). Previously only could specify gamK_CritSel. Specification of gamK1 and gamK2 now included as part of specifying gamModels
* Enhanced to allow for including flow or salinity as an independent variable in gam models, including adding gam4 to default list of gam models evaluated. (**Does** not include updated for computing seasonally averaged/flow[salinity] averaged model in this version.)

baytrends 0.2.7
===========
* Released - 7/20/2017
* Enhanced baytrends to output p-values and estimates of change related to laboratory method changes (“interventions”) in a style that compares method “A” to “B”, “B” to “C”, “C” to “D”, etc. rather than “A” to “B”, “A” to “C”, “A” to “D”, etc.

baytrends 0.2.6
===========
* Released - 4/25/2017
* corrected usage of user specified station file

baytrends 0.2.5
===========
* Released - 3/15/2017
* updated loadData to allow for specifying strings indicating null values, see naChar
* updated multiple functions to address 'no visible binding for global variable' notes
* added @importFrom statements for graphics and stat functions

baytrends 0.2.4
===========
* Released - 2/9/2017
* updated seasonal average model algorithm to be independent of mn.doy
* added algorithm to compute number of knots in s(cyear) term based on record length
* added user ability to set 'select' term in mgcv::gam function to TRUE, FALSE, or algorithm selected
* added user ability to set expectation maximization convergence threshold
* added F-stat evaluation and ANOVA table modification


baytrends 0.2.3
===========
* Released - 11/09/2016
* Documentation updated
* Added default settings to for gam formula for intervention testing
* Added functionality to trim early data where the level of censoring exceeds desired levels
* Added functionality to thin prediction data set to improve speed and reduce the size of the returned results
* loadData: added functionality to convert date-like fields to POSIXct format (see argument convDates)
* Add error trap for when all data associated with dependent variable are NA

baytrends 0.2.2
===========
* Released - 10/17/2016
* Updated graphics for censored data

baytrends 0.2.1
===========
* Original release - 10/13/2016
