---
title: "baytrends, Install from Zip File"
author: "Erik W. Leppo"
date: "`r Sys.time()`"
output: 
  html_notebook:
    toc: yes
    depth: 3
    toc_float: yes
---

# 1. Purpose
Inform current users of `baytrends` R package on update procedure.

# 2. Procedure
1. Download
2. Install
3. Verify

## 2.1. Download
Download the zip file from Google Drive link below.

https://drive.google.com/drive/folders/1q7OdXpM-aJ-OUDPmHUqsUklgc42-aHfd

## 2.2. Install the Package
Depending on the users program environment there are differing methods to install the revised package.  Only one of the following methods needs to be employed.

### 2.2.1. RStudio
Using RStudio the install is done via the toolbar:

1. Tools
2. Install Packages
3. Change "Install from:" to "Package Archive File (.zip;.tar.gz)"
4. Select "Browse" and choose baytrends zip
5. Click "Install" 

### 2.2.2. R GUI
Using the base R GUI the install is done via the toolbar:

1. Packages
2. Install Packages from local file(s)
3. Browse to baytrends zip
4. Select Open

When done R should print to the console:

package 'baytrends' successfully unpacked and MD5 sums checked

### 2.2.3. GitHub
Commands can be typed in to the R console to update from the internet by retrieving the package from its host location on GitHub (a file sharing platform).  This method requires the package `devtools` and should only be used by experienced users.

```{r Install_GitHub, eval=FALSE}
library(devtools)
install_github("leppott/baytrends")
```

## 2.3. Verify Install
To verify the install of `baytrends` type in the commands below into the R console.

This will display all of the help files and version number for the `baytrends` package.

```{r Verify, eval=FALSE}
library(baytrends)
help(package="baytrends")
```

If get any error messages about needing packages (e.g., with a fresh version of R) will need to install those packages as well.  

For example, with a fresh install of R v3.4.3 the following code was necessary to install all of the dependent packages for `baytrends` to function properly.  New package can be included in the myPkgs vector inside the pararentheses.  New packages should be enclosed in quotes and should be preceeded with a comma.

```{r InstallDependancies, eval=FALSE}
myPkgs <- c("lubridate"
            , "dataRetrieval"
            , "digest"
            , "memoise"
            , "pander")
lapply(myPkgs, function(x) install.packages(x))
```