---
title: "R Notebook"
author: "Erik W. Leppo"
date: "`r Sys.time()`"
output: 
  html_notebook:
    toc: yes
    depth: 3
    number_sections: yes
    toc_float: no
---



# Current Version
## Install
Install the latest version of baytrends (v0.3.3) from Jon.

```{r}
install.packages("C:/Users/Erik.Leppo/OneDrive - Tetra Tech, Inc/MyDocs_OneDrive/ChesBay_R/baytrends_20171125/baytrends_0.3.3.tar.gz", repos = NULL, type = "source")
```


## GitHub
1. Unzip the tarball.
2. Add to my GitHub folder as baytrends033.
3. Then load to GitHub as v0.3.3.9001.

# Modify
Remove swmrQW and smwrStats packages.
Repackage and load to GitHub.

# smwr Packages
https://owi.usgs.gov/R/packages.html

## Install packages
Install USGS packages from GitHub.
```{r, EVAL=FALSE}
library(devtools)
install_github("USGS-R/smwrData")
install_github("USGS-R/smwrQW")
install_github("USGS-R/smwrBase")
install_github("USGS-R/smwrStats")
install_github("USGS-R/smwrGraphs")
```

## Functions, smwrQW
Should be able to find with "smwrQW::" but 0 references.

Only a few "smwrBase::"" references searching for "smwr"


DESCRIPTION results.

Package   |USGS Status|baytrends|Base   |Data    |Graphs |QW| Stats
----------|-----------|---------|-------|--------|-------|--|------
smwrBase  |Research   |Suggests |na     |Suggests|-      |- |-
smwrData  |Research   |-        |-      |na      |-      |- |-
smwrGraphs|SUPPORT    |Suggests |DEPENDS|Suggests|na     |- |-
smwrQW    |ORPHAN     |-        |DEPENDS|Suggests|DEPENDS|na|DEPENDS
smwrStats |ORPHAN     |Suggests |DEPENDS|Suggests|DEPENDS|- |na

Not all packages listed on the USGS website below so used the GitHub link for each package to get status.

* https://owi.usgs.gov/R/packages.html
* https://github.com/USGS-R/smwrBase
* https://github.com/USGS-R/smwrData
* https://github.com/USGS-R/smwrGraphs
* https://github.com/USGS-R/smwrQW
* https://github.com/USGS-R/smwrStats


