---
title: "Vignette, QW"
author: "Erik.Leppo@tetratech.com"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette, QW}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
<!-- Data is in vignettes\data folder  -->
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Purpose
Early versions of the `baytrends` package relied on the `smwrQW` package for creating and using QW objects.  The `smwrQW` package has since been orphaned by its maintainer (USGS).  As such the capabilities to create and use a QW object have been ported from the `smwrQW` package into `baytrends`.  This vignette will guide users through the process to convert existing qw objects from the `smwrQW` package to the `baytrends` package (version 0.3.3.9011 or higher).

https://github.com/ldecicco-USGS/smwrQW

https://owi.usgs.gov/R/packages.html#orphan

You will need an internet connection to follow the directions below.

# Process Overview
You will need to install the `smwrQW` package (and other smwr packages), load the packages, then load the object and export the parts.  After loading the object and exporting the parts the packages need to be removed.  Only then can `baytrends` be loaded and a new qw object created from the previously exported parts.

An example using the dataCensored object (as an `smwrQW` qw) is included below.  All the code is meant to be run from start to finish but comments have been added between the steps.  Many parts are automate but running in the steps outlined below will help spot any errors.

~~~~~~~~~~~~~~~~~
* Install and load `smwrQW` packages.
* Load qw object to convert.
* Save object parts.
* Remove `smwrQW` package from computer.
* Recreate qw object from parts as a `baytrends` object.


Items to Automate
* File selection.
    + fname <- file.choose()
    + source(file.choose())
* Checking file "str()" and saving classes.
    + Classes easy.
    + Not sure what to do with things like date/time that come up as "character".
    + May have all the same columns?! 
    + If so that would be *much* easier to automate.
* Loading and removing packages.
    + Shouldn't be much of an issue.
* Dealing with unknown column headers.
    + Should be able to read and save.
    
~~~~~~~~~~~~~~~~~

# Example, dataCensored
Recreate the `smwrQW` qw object dataCensored as a `baytrends` qw object. 

Some variables may be repeated between chunks while others may not.

~~~~~~~~~~~~~~~~~~~~

Original on 2017-12-20 did not export time zone.  Thus when Jon checked the file 2018-01-05 it was missing time zone information (mix of EDT and EST).  Need to export here with the time zone.

format(x, useTZ=TRUE)

switch to v3.4.1 of R to create parts.  OR install smwr* packages to extract the data then remove when build final data file.
~~~~~~~~~~~~~~~~~~~~~~~

## 1. Install Packages
Will need the smwr suite of packages installed before reading dataCensored.  All of the packages are dependant upon each other so need to have all of them installed.  They will be uninstalled in a later step.

Also ensure that have the lastest version of the `baytrends` package.

```{r Example01_Install_Pkgs, eval=FALSE}
require(devtools)
#
# Install swmr packages (see above)
# Detect if package installed then install
myPkg <- c("smwrData", "smwrBase", "smwrGraphs", "smwrStats", "smwrQW")
for (p in myPkg) {##FOR.p.START
  #
  if(!require(p, character.only = TRUE)) {##IF.p.START
    devtools::install_github(paste0("USGS-R/", p))
  }##IF.p.END
  #
}##FOR.p.END
#
if(!require("baytrends")) {devtools::install_github("leppott/baytrends")}
```

## 2. Choose the file to convert.
Load the `smwrQW` package after `baytrends`.

If need to get name of an object hints are here.
http://r.789695.n4.nabble.com/Assigning-a-new-name-to-object-loaded-with-quot-load-quot-td4638144.html

```{r Example02_data0SaveHeader, eval=FALSE}
# Load after baytrends
library(smwrQW)
#
# File chooser to get file
# file.choose() is windows only.  Use tk_choose.files() for other systems.
#fn <- file.choose()
fn <- file.path(path.package("baytrends"), "extdata", "dataCensored__qw.rda")
#
# load qw object
load(fn)
name.qw <- load(fn, verbose=TRUE)
# assign to a generic name so can manipulate (reassign at end)
df.qw <- get(name.qw)
```

## 3. Visually Check Structure
Visually check the object's structure.  There should be no errors. 
```{r, eval=FALSE}
# Visually check object
str(df.qw)
```

## 4. Save Header

~~~~~~~~~~~~~~~~~
 Need to replace dataCensored with get(name.qw)
 Not sure how works with $
~~~~~~~~~~~~~~~~~
```{r Example04_data0SaveHeader, eval=FALSE}
# Ensure date explicitly includes time zone
df.qw$date <- format(df.qw$date, format="%F %T", usetz=TRUE)

# Need export directory - choose.dir is Windows only
myDir <- choose.dir(default=file.path(getwd()), caption="Select folder for qw slot export")
# For non-Windows use tcltk
# library(tcltk)
# tk_choose.dir(getwd(), "Choose a suitable folder")

myDir <- "C:\\Users\\Erik.Leppo\\OneDrive - Tetra Tech, Inc\\MyDocs_OneDrive\\ChesBay_R\\dataCensored_data-raw"

# Output 
# #
df.QW.no <- df.qw[,1:3]
str(df.QW.no)
fn.header <- paste0(name.qw,"00Header.csv")
write.csv(df.QW.no, file.path(myDir, fn.header))
# #
# # have issues
# df.QW.yes <- as.data.frame(dataCensored[,4:16])
# 
fn.all <- paste0(name.qw,".csv")
write.csv(df.qw, file.path(myDir, fn.all))
# seems to have worked

# # Visual check
# x <- read.csv("dataCensored.csv")
# str(x)

myVar <- names(df.qw[-(1:3)])
mySlotNames <- slotNames("qw")

# # To get slot data
# showClass("qw")
# slotNames("qw")
# 
# slot(dataCensored$secchi, "value.codes")

```


## 5. Extract dataCensored slot values
Save each slot in the qw object to its own CSV file.

```{r Example05_data1SaveSlots, eval=FALSE}

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# Loop through and save all data
#library(baytrends) #needs smwrQW library to be present
library(swmwrQW)
df.qw <- df.qw
myVar <- names(df.qw[-(1:3)])
mySlotNames <- slotNames("qw")
#
#
str(df.qw)
# #
df.QW.no <- df.qw[,1:3]
str(df.QW.no)
fn.header <- paste0(name.qw, "_00Header.csv")
write.csv(df.QW.no, file.path(myDir, fn.header))


#
for (i in myVar) {##FOR.i.START
  #
  i.num <- match(i, myVar)
  i.len <- length(myVar)
  #
  for (j in mySlotNames) {##FOR.j.START
    #
    j.num <- match(j, mySlotNames)
    j.len <- length(mySlotNames)
    #
    df.SlotValues <- slot(df.qw[,i], j)
    #
    myFile <- paste(name.qw, i, j, ".csv", sep="_")
    write.csv(df.SlotValues, file.path(myDir, myFile))
    #
    # Report Progress to User
    print(paste0("Saving; item i, ", i," (",i.num," of ",i.len,"), item j, ",j," (",j.num," of ",j.len,")."))
    flush.console()
    #
    }#FOR.j.END
  #
}##FOR.i.END

# Remove smwr* packages 
# myPkg <- c("smwrData", "smwrBase", "smwrGraphs", "smwrStats", "smwrQW")
lapply(myPkg, function(x) remove.packages(x))


```

## 6. Reconstruct the qw data object



```{r Example06_data2Reconstruct, eval=FALSE}
# Reconstruct dataCensored from parts
library(baytrends)
#
# Names
# **** Need to get programaticaly *****
# Should be the same as myVar
# myNames <- c("secchi"
#              , "chla"
#              , "do"
#              , "tn"
#              , "tp"
#              , "po4f"
#              , "pp"
#              , "tdp"
#              , "no23f"
#              , "nh4f"
#              , "tdn"
#              , "pn"
#              , "tss")

myNames <- myVar


# Create DF
#DF <- data.frame(matrix("NA", nrow=7719, ncol=16))
#names(DF) <- myNames
#fn.00 <- paste0(name.qw, "_00.csv")
fn.00 <- paste0(name.qw, "_00Header.csv")

DF <- read.table(file.path(myDir, fn.00), sep=","
                        , header=TRUE, row.names=1
                        , colClasses = "character"
                      )
str(DF)
head(DF)
#
# convert date to POSIXct class (add EST)
#DF[,"date"] <- as.POSIXct(DF[,"date"],tz="EST")
str(DF)
head(DF)
#
# Convert to qw format


```

# Data File Creation Script
Have a separate R script in the "data-raw" folder for generating the "dataCensored" object for the baytrends package from the raw CSV files.

```{r Example99_dataraw_Generate, eval=FALSE}
# Generate data
#
# Erik.Leppo@tetratech.com
# 20171206
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# ensure smwrQW package is not installed
remove.packages("smwrData")
remove.packages("smwrQW")
remove.packages("smwrStats")
remove.packages("smwrGraphs")
remove.packages("smwrBase")
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

{# 0. Prep####
# assume wd is package directory
#wd <- file.path(getwd(),"data-raw")
  
wd <- myDir  
  
  
  

# 1. Generate Data####
# Reconstruct dataCensored from parts
library(baytrends)
#library(baytrends)  # need for as.qw to create class
#
# Names
  # **** Need to get programaticaly *****
myVar <- c("secchi"
             , "chla"
             , "do"
             , "tn"
             , "tp"
             , "po4f"
             , "pp"
             , "tdp"
             , "no23f"
             , "nh4f"
             , "tdn"
             , "pn"
             , "tss")
# Create DF
#DF <- data.frame(matrix("NA", nrow=7719, ncol=16))
#
DF <- read.table(file.path(wd,"dataCensored_00.csv"), sep=","
                 , header=TRUE, row.names=1
                 , colClasses = "character"
                  )
str(DF)
head(DF)
#
# convert date to POSIXct class (add EST)
#DF[,"date"] <- as.POSIXct(DF[,"date"],tz="EST")
DF[,"date"] <- as.POSIXct(DF[,"date"])
str(DF)
head(DF)
#
# Convert to qw format
## loop through each variable and add info
slotNames("qw")
mySlotNames <- c(".Data"
                 , "remark.codes"
                 , "value.codes"
                 , "reporting.level"
                 , "reporting.method"
                 , "reporting.units"
                 , "analyte.method"
                 , "analyte.name"
                 , "rounding"
                 , "unique.code" 
                 , "names") 

#
i <- myVar[1]
}
#
for (i in myVar) {##FOR.i.START
  #
  {
  i.num <- match(i, myVar)
  i.len <- length(myVar)
  #
  # Report Progress to User
  print(paste0("Processing; item i, ", i," (",i.num," of ",i.len,")."))
  flush.console()
  #
  # Load all slotname files
  #myName <- c("values","value2)")
  myFile <- file.path(wd,paste("dataCensored",i,mySlotNames[1],".csv",sep="_"))
    df.var.slot01 <- read.table(myFile, header=TRUE, row.names=1, sep=",")
    
  myName <- mySlotNames[2] 
  myColClass <- "character"
  myFile <- file.path(wd,paste("dataCensored",i,mySlotNames[2],".csv",sep="_"))
    df.var.slot02 <- read.table(myFile, header=TRUE, row.names=1, sep=",", colClasses=myColClass, na.strings="NA")
    names(df.var.slot02) <- myName
  
  # myName <- mySlotNames[3]  
  # myColClass <- "character" 
  # myFile <- file.path(wd,paste("dataCensored",i,mySlotNames[3],".csv",sep="_"))
  #   df.var.slot03 <- read.table(myFile, header=TRUE, row.names=1, sep=",", colClasses=myColClass)
  #   names(df.var.slot03) <- myName
  #   
  # myName <- mySlotNames[4]  
  # myColClass <- "character"
  # myFile <- file.path(wd,paste("dataCensored",i,mySlotNames[4],".csv",sep="_"))
  #   df.var.slot04 <- read.table(myFile, header=TRUE, row.names=1, sep=",", colClasses=myColClass)
  #   names(df.var.slot04) <- myName
  #   
  # myName <- mySlotNames[5]   
  # myColClass <- "character" 
  # myFile <- file.path(wd,paste("dataCensored",i,mySlotNames[5],".csv",sep="_"))
  #   df.var.slot05 <- read.table(myFile, header=TRUE, row.names=1, sep=",", colClasses=myColClass)
  #   names(df.var.slot05) <- myName
  # 
  # myName <- mySlotNames[6]  
  # myColClass <- "character"
  # myFile <- file.path(wd,paste("dataCensored",i,mySlotNames[6],".csv",sep="_"))
  #   df.var.slot06 <- read.table(myFile, header=TRUE, row.names=1, sep=",", colClasses=myColClass)
  #   names(df.var.slot06) <- myName
  # 
  # myName <- mySlotNames[7]  
  # myColClass <- "character"
  # myFile <- file.path(wd,paste("dataCensored",i,mySlotNames[7],".csv",sep="_"))
  #   df.var.slot07 <- read.table(myFile, header=TRUE, row.names=1, sep=",", colClasses=myColClass)
  #   names(df.var.slot07) <- myName
  # 
  # myName <- mySlotNames[8]  
  # myColClass <- "character"
  # myFile <- file.path(wd,paste("dataCensored",i,mySlotNames[8],".csv",sep="_"))
  #   df.var.slot08 <- read.table(myFile, header=TRUE, row.names=1, sep=",", colClasses=myColClass)
  #   names(df.var.slot08) <- myName
  #   
  # # Rounding is not included in as.qw (#09)
  # myName <- mySlotNames[9]  
  # myColClass <- "numeric"
  # # myFile <- file.path(wd,paste("dataCensored",i,mySlotNames[9],".csv",sep="_"))
  # #   df.var.slot09 <- read.table(myFile, header=TRUE, row.names=1, sep=",", colClasses=myColClass)
  # #   names(df.var.slot09) <- myName
  # 
  # myName <- mySlotNames[10]  
  # myColClass <- "character"
  # myFile <- file.path(wd,paste("dataCensored",i,mySlotNames[10],".csv",sep="_"))
  #   df.var.slot10 <- read.table(myFile, header=TRUE, row.names=1, sep=",", colClasses=myColClass)
  #   names(df.var.slot10) <- myName
  #   
  # # names is not included in as.qw (#11)
  # myName <- mySlotNames[11] 
  # myColClass <- "character"
  # # myFile <- file.path(wd,paste("dataCensored",i,mySlotNames[11],".csv",sep="_"))
  # #   df.var.slot11 <- read.table(myFile, header=TRUE, row.names=1, sep=",", colClasses=myColClass)
  # #   names(df.var.slot11) <- myName
  # #
    
  # combine
  df.var.slotData <- cbind(df.var.slot01, df.var.slot02 ) #, df.var.slot03
                           # , df.var.slot04, df.var.slot05, df.var.slot06
                           # , df.var.slot07, df.var.slot08, df.var.slot10)
  # remove to clear memory
  rm(df.var.slot01, df.var.slot02) #, df.var.slot03
      # , df.var.slot04, df.var.slot05, df.var.slot06
      # , df.var.slot07, df.var.slot08, df.var.slot10)

  slotNames("qw")
  getSlots("qw")
  showClass("qw")
  }
  DF[,i] <- as.qw(values       = df.var.slotData[,"values"]
                  , value2           = df.var.slotData[,"value2"]
                  , remark.codes     = df.var.slotData[,"remark.codes"]
                  , value.codes      = ""
                  , reporting.level  = NA_real_
                  , reporting.method = ""
                  , reporting.units  = ""
                  , analyte.method   = ""
                  , analyte.name     = ""
                  , unique.code      = ""
                  )
  #
  DF[,i]@rounding <- c(3,4)  # default is 2,3
  #
  # # define names
  # values.X <- df.var.slotData[,"values"]
  # N.X <- length(values.X)
  # names.X=as.character(seq(N.X))
  # DF[,i]@names <- as.character(seq(N.X))
  # str(DF)
  #View(#
}##FOR.i.END


##~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
# 2. Save as RDA for use in package####
#
#dataCensored <- DF
#setwd("..")
#devtools::use_data(dataCensored, overwrite = TRUE)

myFile.Out <- paste0(name.qw, ".rda")

saveRDS(DF, "xyz.rda")
# reuse file name from beginning.


```

